\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{fancyhdr}
\usepackage{etoolbox}
\usepackage{multicol}
\usepackage{needspace}
\usepackage{tikz}
\usepackage{lastpage}

\pagestyle{fancy}
\fancyhf{}
\rhead{Ethan Ragbir}
\lhead{Resume}
\cfoot{Page \thepage\ of \pageref{LastPage}}

\titleformat{\section}{\Large\bfseries}{}{0em}{}

% Prevent section from being split over pages
\pretocmd{\section}{\Needspace{5\baselineskip}}{}{}
\pretocmd{\subsection}{\Needspace{3\baselineskip}}{}{}

% Full-width section separator line
\newcommand{\sectionline}{\noindent\rule{\linewidth}{0.5mm}}

\begin{document}

\begin{center}
    \textbf{\LARGE Ethan Ragbir} \\
    \vspace{2mm}
    ragbire1@tcnj.edu $\vert$ (718) 607-6955 $\vert$
    \href{https://www.linkedin.com/in/ethan-ragbir-6032b42a3}{linkedin.com/in/ethan-ragbir-6032b42a3} $\vert$ 
    \href{https://github.com/Ethan-Ragbir}{github.com/Ethan-Ragbir} \\
\end{center}

\section*{Education}
\textbf{The College of New Jersey (TCNJ)} \\
\textit{Expected Graduation: 2028} \\
B.S. in Mathematics and Physics \\
\textit{Relevant Coursework:} Classical Mechanics, Electromagnetism, Quantum Physics, Statistical Mechanics, Multivariable Calculus, Differential Equations, Abstract Algebra, Numerical Analysis, Discrete Structures, Machine Learning.



\sectionline

\section*{Experience}
\textbf{Undergraduate Researcher} \hfill \textit{Jun 2025 -- Present} \\
\textit{CERN, Compact Muon Solenoid (CMS) Experiment} \\
Developing a neural-network-based machine learning algorithm to analyze CMS detector data. Enhancing supersymmetry search capabilities beyond 275 GeV. Collaborating with the Rutgers High Energy eXperiment (HEX) group to establish a research team at TCNJ. \\
\textbf{Skills:} Particle Physics, Deep Learning, ROOT

\textbf{Undergraduate Researcher} \hfill \textit{Apr 2025 -- Present} \\
\textit{The College of New Jersey} \\
Studying ice crystal morphology using scanning electron microscopy (SEM) under Dr. Nate Magee. Investigating behavior in extreme environments to improve climate modeling. \\
\textbf{Skills:} SEM, Image Analysis, Climate Physics

\textbf{Research Intern} \hfill \textit{Apr 2025 -- Present} \\
\textit{General Dynamics} \\
Applied machine learning and retrieval-augmented generation (RAG) to optimize jet propulsion dynamics. Integrated real-world datasets with physical models to improve system performance. \\
\textbf{Skills:} Machine Learning, Computational Modeling

\textbf{Machine Learning Engineer Intern} \hfill \textit{Jan 2025 -- May 2025} \\
\textit{Stealth Startup} \\
Contributed to large language model (LLM) NLP systems under non-disclosure agreement. Supported model training and deployment pipelines. \\
\textbf{Skills:} Natural Language Processing, Python, Production ML

\textbf{Matroid Theory Researcher} \hfill \textit{Jun 2024 -- Sep 2024} \\
\textit{Princeton University} \\
Analyzed matroid structures in discrete mathematics for optimization and network reliability. Applied concepts to theoretical computer science problems. \\
\textbf{Skills:} Discrete Math, Optimization, Proof Techniques

\textbf{Software Engineer Intern} \hfill \textit{Apr 2023 -- Dec 2023} \\
\textit{New Jersey Institute of Technology (NJIT)} \\
Maintained backend systems and contributed to scalable application development. Built RESTful APIs under faculty supervision. \\
\textbf{Skills:} Software Engineering, Python, Git

\sectionline

\section*{Technical Skills}
\textbf{Languages:} Python, C++, Java, MATLAB, LaTeX \\
\textbf{Tools / Libraries:} Git, TensorFlow, PyTorch, CERN ROOT, OpenCV, LangChain, VS Code, Firebase, PostgreSQL, Linux, Bash, Docker, Conda, Jupyter, Pandas, NumPy

\sectionline

\section*{Projects}
\textbf{Particle Detection with Neural Networks} \hfill \textit{CERN, 2025} \\
Built a classifier to identify particle interactions in CMS detector data. Integrated CERN ROOT preprocessing and TensorFlow training workflows.

\textbf{Geophysical Ice Imaging Toolkit} \hfill \textit{TCNJ, 2025} \\
Automated extraction of morphological features of ice crystals using SEM. Developed batch-processing pipeline to support climate model research.

\textbf{Monte Carlo Jet Propulsion Simulator} \hfill \textit{General Dynamics, 2025} \\
Simulated jet propulsion dynamics with Monte Carlo methods. Integrated physics-informed ML to analyze flow stability.

\textbf{Matroid Optimizer} \hfill \textit{Princeton University, 2024} \\
Developed Python tool for evaluating matroid rank, closure, and independence properties. Used in optimization and graph theory research.

\sectionline

\section*{Extracurricular Activities}
\textbf{Putnam Competition Team} \hfill \textit{Since Fall 2024} \\
The College of New Jersey \\
Compete in the William Lowell Putnam Mathematical Competition with intensive problem-solving training in advanced mathematics.

\textbf{Mathematical Olympiad Prep Team} \hfill \textit{ Fall 2022 - June 2024} \\
Frankloing  \\
Weekly sessions in number theory, combinatorics, and geometry to prepare for national mathematical competitions.

\textbf{Chess Club} \hfill \textit{Since Fall 2024]} \\
The College of New Jersey \\
Participate in weekly tournaments and rated practice. Studying classical openings and tactics.

\sectionline

\section*{Volunteer Experience}
\textbf{Bonner Community Scholar} \hfill \textit{Aug 2024 -- Present} \\
The College of New Jersey \\
Complete 300+ community service hours per academic year. Engage in social justice education, civic engagement, and public service projects.

\textbf{Red Cross Volunteer Representative} \hfill \textit{2024 -- Present} \\
American Red Cross \\
Serve as a youth representative for disaster relief coordination and public outreach campaigns.

\sectionline

\section*{Professional Memberships}
\textbf{Institute of Electrical and Electronics Engineers (IEEE)} \hfill \textit{Feb 2025 -- Present} \\
\textbf{American Physical Society (APS)} \hfill \textit{2025 -- Present} \\
\textbf{Society for Industrial and Applied Mathematics (SIAM)} \hfill \textit{2025 -- Present}

\end{document}
